---
title: "Figure 5"
author: "Sam Herr, Mike Gore"
email: "skh77@cornell.edu"
date: "2024-04-19"
output: html_document
---

This R markdown file is for Figure 5

The outline for the code chunks:
1. Packages
2. Figure 5a - includes analysis and visualization
3. Figure 5b - include analysis and visualization
4. Figure S13
5. Figure S15

```{r setup, include=FALSE}
library(tidyverse)
library(multcomp)
library(gdata)
library(ggplot2)
library(gridExtra)
library(data.table)
library(agricolae)
library(readxl)
library(car)
```


Figure 5a code chunk:
input: figure5a_data.csv
data: 2019 Cornell Field experiment 
Tissue type: Mature Kernels

```{r Figure 5a}
setwd("~/Documents/GoreLab/POR1_2/Light_dark_exp/scripts")
#Plot metabolites from 2019 field experiment
metabolites <- read.csv("../data/figure5a_data.csv")

#select total tocopherols, tocotrienols, and carotenoids
metabolites <- metabolites[,c(1,2,3,10,11,13,14)]
colnames(metabolites)[4:6] <- c( "Total Tocotrienols","Total Tocopherols", "Total Carotenoids")

#prepare for data for plotting
m_plotting <- metabolites %>% pivot_longer(c(`Total Tocotrienols`, `Total Tocopherols`, `Total Carotenoids`) )
colnames(m_plotting)[3] <- c("por")
colnames(m_plotting)[4] <- c("Genotype")

#prepare data for statistical tests
traits <- colnames(metabolites)[4:6]
results_list <- list()

#This for loop checks for outliers and performs Tukey's HSD to compare all mutants
for ( i in 1: length(traits)){
  #data format
  x <-  unlist(as.vector( metabolites[,traits[i]]))
  df <- data.frame("TT" = x, "geno" = as.factor(metabolites$geno), "family"= as.factor(metabolites$Family), "combine" = as.factor(paste(metabolites$geno, "_",metabolites$Family)))
  #df <- df[,c(1,2)]
  #df$geno <- as.factor(df$geno)
 # print(traits[i])
  print(leveneTest(TT~ geno,df))
  print(leveneTest(TT~ family,df))
 # print(shapiro.test(residuals(lm(TT~geno*family,df))))
  options(contrasts = c("contr.sum", "contr.poly"))
  #statistical tests
  model <- lm(TT~ family* geno, data = df)
  x <- Anova(model, data = df, type = "III")
  summary(x)
  #plot(x)
  #print(summary(x))
  #no outliers found
  print(outlierTest(x, cutoff=0.05, order=TRUE))
  comparison <- HSD.test(model, "geno", group=TRUE, unbalanced = T)
  #print(summary(gl))
  tuk.cld2 <- comparison$groups[,2]
  result_df <- data.frame(
    Genotype = rownames(comparison$groups),
    name = rep(traits[i],5),
    cld = tuk.cld2
  )
  
  # Store the result data frame in the list
  results_list[[i]] <- result_df
  #diff <- m[, "p adj"]
  
}



#prepare data for figures for manuscript
tukey <- data.table::rbindlist(results_list)
#For setting maximum y-value in visualiztion
max_values <- aggregate(value ~ name, data = m_plotting, FUN = max)
tukey_df <- merge(tukey, max_values, by = "name", suffixes = c("", "_max"))

#format for plot
m_plotting$Genotype <- gsub("\\+---", "por1/+;por2/por2", m_plotting$Genotype)
m_plotting$Genotype <- gsub("--\\+-", "por1/por1;por2/+", m_plotting$Genotype)
m_plotting$Genotype <- gsub("----", "por1/por1;por2/por2", m_plotting$Genotype)
m_plotting$Genotype <- gsub("\\+\\+--", "por2/por2", m_plotting$Genotype)
m_plotting$Genotype <- gsub("--\\+\\+", "por1/por1", m_plotting$Genotype)
m_plotting$Genotype <- gsub("\\+\\+\\+\\+", "WT",m_plotting$Genotype)

tukey_df$Genotype <- gsub("\\+---", "por1/+;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("--\\+-", "por1/por1;por2/+", tukey_df$Genotype)
tukey_df$Genotype <- gsub("----", "por1/por1;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("\\+\\+--", "por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("--\\+\\+", "por1/por1", tukey_df$Genotype)
tukey_df$Genotype <- gsub("\\+\\+\\+\\+", "WT",tukey_df$Genotype)
tukey_df$name <- factor(tukey_df$name, level= c("Total Carotenoids" ,"Total Tocotrienols","Total Tocopherols"))

m_plotting$Genotype <- factor(m_plotting$Genotype, level=c('WT', 'por1/por1', 'por2/por2', 'por1/+;por2/por2','por1/por1;por2/+', 'por1/por1;por2/por2'))
m_plotting$name <- factor(m_plotting$name, level=c('Total Carotenoids', 'Total Tocotrienols', 'Total Tocopherols'))

ggplot(m_plotting, aes(x = Genotype, y=value, fill = Genotype)) + 
              geom_boxplot() +
  geom_text(data = tukey_df, aes(Genotype, y =value, label = cld),  vjust = -0.5) +
     geom_point(aes(colour = Family)) +
  facet_wrap(~name, scales = "free_y") +
scale_fill_manual(values =c("#004D40","#004D40","#004D40",  "greenyellow", "#004D40"))+
  scale_color_manual(values =c("red", "black"))+
  theme_bw()+
  labs('')+
    scale_y_continuous(limits = c(0, NA)) +

  ylab("Concentration")+
  xlab("") +
  theme(
    legend.text = element_text(size = 10),
    plot.title.position = "plot",
    panel.spacing = unit(3, "lines"),
    strip.text = element_text(size = 20),
    axis.text.x = element_text(size=15,face = "italic",colour = "black",angle = 45,hjust = 1, vjust = 1),
    text = element_text(family = "Helvetica"),
    axis.text.y = element_text(size=10,face="bold",colour = "black",angle = 0),
    strip.text.x = element_text(size = 12,face="bold",color="black", angle =360,family='sans'))


ggsave("Figure_5a_interaction.png",width = 10, height =8)



calculate_percent_increase <- function(original_value, new_value) {
  # Calculate the difference
  difference <- new_value - original_value
  
  # Calculate percent increase
  percent_increase <- (difference / original_value) * 100
  
  # Return the percent increase
  return(mean(percent_increase))
}



```

Figure 5b code chunk:
input: figure5b_data.csv
data: 2020 Cornell Greenhouse experiment 
Tissue type: Mature Kernels

```{r Figure 5b}
### data from 2022 analysis for 20GH mature seeds
re <-  read_xlsx("../data/figure5b_data.xlsx", sheet = 2)[,-c(2,7:9)]

#format data
re <- re[,-c(1:3,6:11,14)]
colnames(re) <- c("geno", "Genotype", "Total Tocotrienols", "Total Tocopherols", "Total Carotenoids")
traits <- colnames(re)[3:5]
results_list <- list()

#Perform Tukey's HSD and check for outliers
#outputs dataframe that contains plotting information
for ( i in 1: length(traits)){
  x <-  unlist(as.vector( re[,traits[i]]))
  print(traits[i])
  df <- data.frame("TT" = x, "geno" = re$Genotype)
  
  df <- df[,c(1,2)]
  df$geno <- as.factor(df$geno)
  print(leveneTest(TT~ geno,df))
  print(shapiro.test(residuals(lm(TT~geno,df))))

  
  model <- lm(TT~geno,df)
  # perform aov test,type 1 as we only have one term
  x <- aov(TT~ geno, df)
  print(outlierTest(x, cutoff=0.05, order=TRUE))
  
  # Calculate critical value from t-distribution

  #perform Tukey HSD and get letters for plotting
  m <- TukeyHSD(x)
  comparison <- HSD.test(model, "geno", group=TRUE, unbalanced = T)
  #print(summary(gl))
  tuk.cld2 <- comparison$groups[,2]
  result_df <- data.frame(
    Genotype = rownames(comparison$groups),
    name = rep(traits[i],4),
    cld = tuk.cld2
  )
  
  # Store the result data frame in the list
  results_list[[i]] <- result_df
  
}
write.csv(data.table::rbindlist(tukey_list), "Tukey_results_2020_GH_mature.csv")
write.csv(data.table::rbindlist(anova_list), "ANOVA_results_2020_GH_mature.csv")
#format for plot
tukey <- data.table::rbindlist(results_list)
re_m <- melt(as.data.table(re), id.vars = c("geno","Genotype"))
colnames(re_m)[3:4] <- c("name","value")
re_m$name <- factor(re_m$name, level= c("Total Carotenoids" ,"Total Tocotrienols","Total Tocopherols"))
max_values <- aggregate(value ~ name, data = re_m, FUN = max)
tukey_df <- merge(tukey, max_values, by = "name", suffixes = c("", "_max"))

#switch notation in both annotation (tukey) and dataframe (re_m)
tukey_df$Genotype <- gsub("\\+---", "por1/+;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("----", "por1/por1;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("\\+\\+--", "por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("\\+\\+\\+\\+", "WT",tukey_df$Genotype)
re_m$Genotype <- gsub("\\+---", "por1/+;por2/por2", re_m$Genotype)
re_m$Genotype <- gsub("----", "por1/por1;por2/por2", re_m$Genotype)
re_m$Genotype <- gsub("\\+\\+--", "por2/por2", re_m$Genotype)
re_m$Genotype <- gsub("\\+\\+\\+\\+", "WT",re_m$Genotype)

#format for plot
re_m$Genotype <- factor(re_m$Genotype, level=c('WT',  'por2/por2','por1/+;por2/por2',  'por1/por1;por2/por2'  ))
tukey_df$Genotype <- factor(tukey_df$Genotype, level=c('WT',  'por2/por2','por1/+;por2/por2',  'por1/por1;por2/por2'  ))
tukey_df$name <- factor(tukey_df$name, level= c("Total Carotenoids" ,"Total Tocotrienols","Total Tocopherols"))
re_m$name <- factor(re_m$name, level= c("Total Carotenoids" ,"Total Tocotrienols","Total Tocopherols"))

ggplot(re_m, aes(x = factor(Genotype), y=value)) +
  geom_boxplot(aes( fill = Genotype), show.legend = F) +
  geom_point() +
  geom_text(data = tukey_df, aes(x = Genotype, y =value, label = cld),  vjust = -0.5) +
  scale_y_continuous(limits = c(0, NA)) +
  
  facet_wrap(~name, scales = "free_y") +
  scale_fill_manual(values =c( "#004D40","#004D40" , "greenyellow","#FFC107"))+
  
  theme_bw()+
  labs('')+
  ylab("Concentration")+
  xlab("") +
  theme(
    legend.text = element_text(size = 10),
    plot.title.position = "plot",
    panel.spacing = unit(3, "lines"),
    strip.text = element_text(size = 20),
    axis.text.x = element_text(size=18,face = "italic",colour = "black",angle = 45,hjust = 1, vjust = 1),
    text = element_text(family = "Helvetica"),
    axis.text.y = element_text(size=10,face="bold",colour = "black",angle = 0),
    strip.text.x = element_text(size = 15,face="bold",color="black", angle =360,family='sans'))


ggsave("Figure_5b.png",width = 10, height =10)

re_m <- re_m[,-1]
x <- re_m %>% group_by(Genotype, name) %>% dplyr::summarise(mean_values = mean(value))

```

Supplemental figures:

Figure S12 code chunk:
input: figure5a_data.csv
data: 2019 Cornell Field experiment 
Tissue type: Mature Kernels
```{r Figure S12}

#formatting function for plotting names
replace_with_greek <- function(input_string) {
  # Replace 'a' with 'α' (alpha)
  input_string <- gsub("^a.", "α-", input_string)
  
  # Replace 'd' with 'δ' (delta)
  input_string <- gsub("^d.", "δ-", input_string)
  
  # Replace 'g' with 'γ' (gamma)
  input_string <- gsub("^g.", "γ-", input_string)
  input_string <- gsub("^B.", "β-", input_string)
  
  
  input_string <- gsub("l[.]TT3", "l Tocochromanol", input_string)
  input_string <- gsub("Total[.]Tocotrienols", "Total Tocotrienols", input_string)
  
  input_string <- gsub("T3$", "Tocotrienol", input_string)
  
  input_string <- gsub("Total[.]Tocopherols", "Total Tocopherols", input_string)
  input_string <- gsub("-T$", "-Tocopherol", input_string)
  
  # Replace "T" with "Tocopherol"
    return(input_string)

} 
  
setwd("~/Documents/GoreLab/POR1_2/Light_dark_exp/scripts")
#Plot metabolites from 2019 field experiment
metabolites <- read.csv("../data/figure5a_data.csv")

#select total tocopherols, tocotrienols, and carotenoids

#prepare for data for plotting

#prepare data for statistical tests
traits <- colnames(metabolites)[4:12]
results_list <- list()
anova_list <- list()
tukey_list <- list()
#This for loop checks for outliers and performs Tukey's HSD to compare all mutants
for ( i in 1: length(traits)){
  #data format
  x <-  unlist(as.vector( metabolites[,traits[i]]))
  df <- data.frame("TT" = as.numeric(x), "Genotype" = as.factor(metabolites$geno), "Family"= as.factor(metabolites$Family), "combine" = as.factor(paste(metabolites$geno, "_",metabolites$Family)))

  #print(leveneTest(TT~ Genotype,df))
  #print(leveneTest(TT~ family,df))
  #print(shapiro.test(residuals(lm(TT~Genotype*family,df))))
  
  #statistical tests
  options(contrasts = c("contr.sum", "contr.poly"))
  model <- lm(TT~ Family* Genotype, data = df)
  x <- Anova(model, data = df, type = "III")
  print(outlierTest(model, cutoff=0.05, order=TRUE))

  x$trait <- rep(traits[i],5)
  x$comparisons <- row.names(x)

  anova_list[[i]] <- x
  comparison <- HSD.test(model, "Genotype", group=F, unbalanced = T)
  tukey_df <- comparison$comparison
  tukey_df$trait <- rep(traits[i],10)
  tukey_df$comparison <- row.names(tukey_df)
  tukey_list[[i]] <- tukey_df
  #print(summary(gl))
   comparison <- HSD.test(model, "Genotype", group=T, unbalanced = T)
  tuk.cld2 <- comparison$groups[,2]
  result_df <- data.frame(
    Genotype = rownames(comparison$groups),
    name = rep(traits[i],5),
    cld = tuk.cld2
  )
  
  # Store the result data frame in the list
  results_list[[i]] <- result_df

}

#For Supplemental Tables
write.csv(data.table::rbindlist(tukey_list), "Tukey_results_2019_mature.csv")
write.csv(data.table::rbindlist(anova_list), "ANOVA_results_2019_mature.csv")


#Creating data frames used in visualizations
tukey <- data.table::rbindlist(results_list)
metabolites <- metabolites %>% select(!c(Barcode,Genotype))
m_plotting <- metabolites %>% pivot_longer(!c(Family, geno))
#set max value to set y limitations
max_values <- aggregate(value ~ name, data = m_plotting, FUN = max)
tukey_df <- merge(tukey, max_values, by = "name", suffixes = c("", "_max"))


#format for plot
m_plotting$Genotype <- m_plotting$geno
m_plotting$Genotype <- gsub("\\+---", "por1/+;por2/por2", m_plotting$Genotype)
m_plotting$Genotype  <- gsub("--\\+-", "por1/por1;por2/+", m_plotting$Genotype)
m_plotting$Genotype  <- gsub("----", "por1/por1;por2/por2", m_plotting$Genotype)
m_plotting$Genotype  <- gsub("\\+\\+--", "por2/por2", m_plotting$Genotype)
m_plotting$Genotype  <- gsub("--\\+\\+", "por1/por1", m_plotting$Genotype)
m_plotting$Genotype  <- gsub("\\+\\+\\+\\+", "WT",m_plotting$Genotype)

tukey_df$Genotype <- gsub("\\+---", "por1/+;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("--\\+-", "por1/por1;por2/+", tukey_df$Genotype)
tukey_df$Genotype <- gsub("----", "por1/por1;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("\\+\\+--", "por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("--\\+\\+", "por1/por1", tukey_df$Genotype)
tukey_df$Genotype <- gsub("\\+\\+\\+\\+", "WT",tukey_df$Genotype)

tukey_df$name <- replace_with_greek(tukey_df$name)
m_plotting$name <- replace_with_greek(m_plotting$name)



m_plotting$Genotype <- factor(m_plotting$Genotype, level=c('WT', 'por1/por1', 'por2/por2', 'por1/+;por2/por2','por1/por1;por2/+', 'por1/por1;por2/por2'))

tukey_df$Genotype <- factor(tukey_df$Genotype, level=c('WT', 'por1/por1', 'por2/por2', 'por1/+;por2/por2','por1/por1;por2/+', 'por1/por1;por2/por2'))

tukey_df <- tukey_df %>% filter(name != "Total.Tocochromanols")
m_plotting <- m_plotting %>% filter(!(name %in% c("Total.Tocochromanols", "Total.Carots")))

m_plotting$name <- factor(m_plotting$name, levels = c( "α-Tocotrienol" ,"δ-Tocotrienol","γ-Tocotrienol", "Total Tocotrienols", "α-Tocopherol" , "δ-Tocopherol" ,"γ-Tocopherol",      "Total Tocopherols"))
tukey_df$name <- factor(tukey_df$name, levels = c( "α-Tocotrienol" ,"δ-Tocotrienol","γ-Tocotrienol", "Total Tocotrienols", "α-Tocopherol" , "δ-Tocopherol" ,"γ-Tocopherol",      "Total Tocopherols"))


ggplot(m_plotting, aes(x = Genotype , y=value, fill = Genotype )) + 
              geom_boxplot(show.legend = F) +
  geom_point(aes(color =Family ), show.legend = F)+
  geom_text(data = tukey_df, aes(x = Genotype, y =1.1*value, label = cld),position=position_dodge(width=0.9), color = "black", family= "sans", size = 5)  +
  facet_wrap(~name, scales = "free_y", ncol =4) +
scale_fill_manual(values =c("#004D40","#004D40","#004D40", "#004D40",  "greenyellow"))+
  scale_color_manual(values =c("red", "black"))+
    scale_y_continuous(limits = c(0, NA)) +

  theme_bw()+
  labs('')+
  ylab("Concentration")+
  xlab("") +
  theme(
   legend.text = element_text(size = 10),
          plot.title.position = "plot",
        axis.title=element_text(size=30),
        panel.spacing = unit(4, "lines"),
        strip.text = element_text(size = 20),
               axis.text.x = element_text(size=20,face = "italic",colour = "black",angle = 45,hjust = 1, vjust = 1),
        text = element_text(family = "Helvetica"),
        axis.text.y = element_text(size=15,face="bold",colour = "black",angle = 0),
   legend.key.size = unit(8, 'cm'))  


ggsave("Figure_S13.png",width = 24, height =12)

```

Figure S15 code chunk:
input: figure5b_data.csv
data: 2020 Cornell Greenhouse experiment 
Tissue type: Mature Kernels

```{r Figure S15}

#formatting function for plotting names
replace_with_greek <- function(input_string) {
  # Replace 'a' with 'α' (alpha)
  input_string <- gsub("^a.", "α-", input_string)
  
  # Replace 'd' with 'δ' (delta)
  input_string <- gsub("^d.", "δ-", input_string)
  
  # Replace 'g' with 'γ' (gamma)
  input_string <- gsub("^g.", "γ-", input_string)
  input_string <- gsub("^B.", "β-", input_string)
  
  
  input_string <- gsub("l[.]TT3", "l Tocochromanol", input_string)
  input_string <- gsub("T3$", "Tocotrienol", input_string)

  input_string <- gsub("Total[.]Tocotrienol", "Total Tocotrienols", input_string)
  
  
  input_string <- gsub("Total[.]T", "Total Tocopherols", input_string)
  input_string <- gsub("-T$", "-Tocopherol", input_string)
  
  # Replace "T" with "Tocopherol"
    return(input_string)

} 
  
### data from 2022 analysis for 20GH mature seeds
metabolites <-  read_xlsx("../data/figure5b_data.xlsx", sheet = 2)[,-c(2,7:9)]

#format data
metabolites <- metabolites[,-c(1:3)]
colnames(metabolites)[1:2] <- c("geno", "Genotype")
traits <- colnames(metabolites)[3:12]
results_list <- list()
anova_list <- list()
tukey_list <- list()
#Perform Tukey's HSD and check for outliers
#outputs dataframe that contains plotting information
for ( i in 1: length(traits)){
  x <-  unlist(as.vector( metabolites[,traits[i]]))
  print(traits[i])
  df <- data.frame("TT" = x, "geno" = metabolites$geno)
  
  df <- df[,c(1,2)]
  df$geno <- as.factor(df$geno)
  print(leveneTest(TT~ geno,df))
  print(shapiro.test(residuals(lm(TT~geno,df))))

  options(contrasts = c("contr.sum", "contr.poly"))
  model <- lm(TT~geno,df)
  # perform aov test
  x <- car::Anova(model, type = "III")

  #print(outlierTest(x, cutoff=0.05, order=TRUE))
  x$trait <- rep(traits[i],3)
  x$comparisons <- row.names(x)

  anova_list[[i]] <- x
  # Calculate critical value from t-distribution

  #perform Tukey HSD and get values for table
  comparison <- HSD.test(model, trt = "geno", group=F, unbalanced = T)
  tukey_df <- comparison$comparison
  tukey_df$trait <- rep(traits[i],6)
  tukey_df$comparison <- row.names(tukey_df)
  tukey_list[[i]] <- tukey_df
  #perform Tukey HSD and get letters for F
  comparison <- HSD.test(model, trt = "geno", group=T, unbalanced = T)
  tuk.cld2 <- comparison$groups[,2]
  result_df <- data.frame(
    Genotype = rownames(comparison$groups),
    name = rep(traits[i],4),
    cld = tuk.cld2
  )
  
  # Store the result data frame in the list
  results_list[[i]] <- result_df
  
}

#tables for dataframes
write.csv(data.table::rbindlist(tukey_list), "Tukey_results_2020_GH_mature.csv")
write.csv(data.table::rbindlist(anova_list), "ANOVA_results_2020_GH_mature.csv")


#format for plot
tukey <- data.table::rbindlist(results_list)


metabolites_corrected <- melt(as.data.table(metabolites), id.vars = c("geno","Genotype"))
colnames(metabolites_corrected)[3:4] <- c("name","value")
metabolites_corrected$name <- replace_with_greek(metabolites_corrected$name)
max_values <- aggregate(value ~ name, data = metabolites_corrected, FUN = max)
tukey$name <- replace_with_greek(tukey$name)
tukey_df <- merge(tukey, max_values, by = "name", suffixes = c("", "_max"))

#switch notation in both annotation (tukey) and dataframe (metabolites_corrected)
tukey_df$Genotype <- gsub("POR1por1por2por2", "por1/+;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("por1por1por2por2", "por1/por1;por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("POR1POR1por2por2", "por2/por2", tukey_df$Genotype)
tukey_df$Genotype <- gsub("POR1POR1POR2POR2", "WT",tukey_df$Genotype)
metabolites_corrected$Genotype <- gsub("\\+---", "por1/+;por2/por2", metabolites_corrected$Genotype)
metabolites_corrected$Genotype <- gsub("----", "por1/por1;por2/por2", metabolites_corrected$Genotype)
metabolites_corrected$Genotype <- gsub("\\+\\+--", "por2/por2", metabolites_corrected$Genotype)
metabolites_corrected$Genotype <- gsub("\\+\\+\\+\\+", "WT",metabolites_corrected$Genotype)

#format for plot
metabolites_corrected$Genotype <- factor(metabolites_corrected$Genotype, level=c('WT',  'por2/por2','por1/+;por2/por2',  'por1/por1;por2/por2'  ))
tukey_df$Genotype <- factor(tukey_df$Genotype, level=c('WT',  'por2/por2','por1/+;por2/por2',  'por1/por1;por2/por2'  ))

metabolites_corrected <- metabolites_corrected %>% filter()

tukey_df <- tukey_df %>% filter(!(name %in% c("Total Tocochromanol", "Total.Carots")))
metabolites_corrected <- metabolites_corrected %>% filter(!(name %in% c("Total Tocochromanol", "Total.Carots")))
tukey_df$value <- 1.1 *tukey_df$value


metabolites_corrected$name <- factor(metabolites_corrected$name, levels = c( "α-Tocotrienol" ,"δ-Tocotrienol","γ-Tocotrienol", "Total Tocotrienols", "α-Tocopherol" , "δ-Tocopherol" ,"γ-Tocopherol",   "Total Tocopherols"))
tukey_df$name <- factor(tukey_df$name, levels = c( "α-Tocotrienol" ,"δ-Tocotrienol","γ-Tocotrienol", "Total Tocotrienols", "α-Tocopherol" , "δ-Tocopherol" ,"γ-Tocopherol",     "Total Tocopherols"))


ggplot(metabolites_corrected, aes(x = factor(Genotype), y=value)) +
  geom_boxplot(aes( fill = Genotype), show.legend = F) +
  geom_point() +
  geom_text(data = tukey_df, aes(x = Genotype, y =value, label = cld),position=position_dodge(width=0.9), color = a"black", family= "sans", size = 5) +
  scale_y_continuous(limits = c(0, NA)) +
  
  facet_wrap(~name, scales = "free_y", ncol =4) +
  scale_fill_manual(values =c( "#004D40","#004D40" , "greenyellow","#FFC107"))+
  
  theme_bw()+
  labs('')+
  ylab("Concentration")+
  xlab("") +
  theme(
   legend.text = element_text(size = 10),
          plot.title.position = "plot",
        axis.title=element_text(size=30),
        panel.spacing = unit(4, "lines"),
        strip.text = element_text(size = 20),
               axis.text.x = element_text(size=20,face = "italic",colour = "black",angle = 45,hjust = 1, vjust = 1),
        text = element_text(family = "Helvetica"),
        axis.text.y = element_text(size=15,face="bold",colour = "black",angle = 0),
   legend.key.size = unit(8, 'cm'))   


ggsave("Figure_S15.png",width = 24, height =12)

```