---
title: "Genetic_KO_metabolite_plots"
author: "Sam Herr, Michael Gore"
email: "skh77@cornell.edu"
output: html_document
date: "2023-08-18"
---
This R markdown file is for Figure 6 

The outline for the code chunks:
1. Packages
2. Figure 6a - includes analysis and visualization
3. Figure 6b - include analysis and visualization
4. Percent increase code
5. supplemental figures

Code chunk 2 and 3 are copied and pasted code but analyze different tissue types. Only code chunk 2 is commented thoroughly. Copy and pasting was the easier option at the time to do that instead write things into functions. Code could be much better written as well

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gdata)
library(data.table)
library(readxl)
library(tidyverse)
library(car)
library(DescTools)
library(patchwork)
library(multcomp)
library(agricolae)
library(rstatix)

#formatting function for plotting names
replace_with_greek <- function(input_string) {
  # Replace 'a' with 'α' (alpha)
  input_string <- gsub("^a.", "α-", input_string)
  
  # Replace 'd' with 'δ' (delta)
  input_string <- gsub("^d.", "δ-", input_string)
  
  # Replace 'g' with 'γ' (gamma)
  input_string <- gsub("^g.", "γ-", input_string)
  input_string <- gsub("^B.", "β-", input_string)
  
  
  input_string <- gsub("l.TT3", "l Tocochromanol", input_string)
  input_string <- gsub("Total[.]T3", "Total Tocotrienols", input_string)
  
  input_string <- gsub("T3$", "Tocotrienol", input_string)
  
  input_string <- gsub("Total[.]T", "Total Tocopherols", input_string)
  input_string <- gsub("-T$", "-Tocopherol", input_string)
  
  # Replace "T" with "Tocopherol"
  
  
  return(input_string)
}
```

Figure 6a code chunk:
input: figure6_data.csv
data: 2020  Greenhouse experiment 
Tissue type: 24 DAP embryo tissue 

```{r figure 6a}
#Read in data and prepare dataframes
metabolites_df <-   read_xlsx("../data/figure6_data.xlsx", sheet = 2)[,-c(1,5)]
tissues <- c("9.3-41_Embryo","9.3-41_Endosperm","9.3-5_Embryo","9.3-5_Endosperm")
traits <- c("a.T", "d.T", "g.T", "a.T3", "d.T3", "g.T3", "Total.T", "Total.T3", "Total.TT3","Chla", "Total.Carots")

#format names for figures
metabolites_df$Genotype <- gsub("-","*",metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\+\\*\\*\\*", "por1/+;por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\+\\*", "por1/por1;por2/+", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\*\\*", "por1/por1;por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\+\\+\\*\\*", "por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\+\\+", "por1/por1", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\+\\+\\+\\+", "WT",metabolites_df$Genotype)

#lists will be filled in the below for loop
results_list <- list()
anova_list <- list()
tukey_list <- list()

#get Embryo tissue
metabolites_df <- metabolites_df[metabolites_df$Tissue %in% c("9.3-41_Embryo","9.3-5_Embryo"),]
colnames(metabolites_df)[1] <- "Family"

#For loop, check's models assumption
#perform ANOVA, Tukey's HSD on every trait wanted
#Check for outliers using studentized residuals 
for ( i in 1: length(traits)){
  #get trait (i.e. tocochromonal) and tissue type
  x <-  unlist(as.vector( metabolites_df[,traits[i]]))

  df <- data.frame("TT" = x, "Genotype" = metabolites_df$Genotype, "Family" = as.factor(metabolites_df$Family), rep = as.factor(metabolites_df$Rep))
  df$Genotype <- as.factor(df$Genotype)
  print(df$Genotype)
  print(traits[i])
  
  #check equality of variances with Levene's test
  #print(leveneTest(TT~ Genotype,df))
  
  # Identify outliers
  model <- lm(TT~ Family*Genotype,df)
  options(contrasts = c("contr.sum", "contr.poly"))
  
  outliers <- outlierTest(model, cutoff=0.05, order=TRUE, label = rownames(df))
  #remove outliers if they exist
  if (outliers$signif) {
    clean_df <- df[!rownames(df) %in% names(outliers$bonf.p < 0.01), ]
    model <- lm(TT~ Genotype, clean_df)
    #statistical tests
    model <- lm(TT~ Family*Genotype,df)
    #ANOVA
    anova_mod <- Anova(model, data = df, type = "III")
    summary(anova_mod)
    anova_mod$trait <- rep(traits[i],5)
    anova_mod$comparisons <- row.names(anova_mod)
    anova_list[[i]] <- anova_mod
   #Tukey's HSD for table
    comparison <- HSD.test(model, "Genotype", group=F, unbalanced = T)
    tukey_df <- comparison$comparison
    tukey_df$trait <- rep(traits[i],6)
    tukey_df$comparison <- row.names(tukey_df)
    tukey_list[[i]] <- tukey_df
  #print(summary(gl))
    #Tukey's HSD for figures
    comparison <- HSD.test(model, "Genotype", group=TRUE)
  #print(summary(gl))
    tuk.cld2 <- comparison$groups[,2]
    result_df <- data.frame(
      Genotype = rownames(comparison$groups),
      name = rep(traits[i],4),
      cld = tuk.cld2
    )
    # Store the result data frame in the list
    removed_results_list[[i]] <- result_df
    next
  }
   #same analysis as in if the statement, run if not outliers are significant
    anova_mod <- Anova(model, data = df, type = "III")
    anova_mod$trait <- rep(traits[i],5)
    anova_mod$comparisons <- row.names(x)
    anova_list[[i]] <- anova_mod
    comparison <- HSD.test(model, "Genotype", group=F, unbalanced = T)
    tukey_df <- comparison$comparison
    tukey_df$trait <- rep(traits[i],6)
    tukey_df$comparison <- row.names(tukey_df)
    tukey_list[[i]] <- tukey_df
  #perform Tukey HSD and get letters for plotting
  comparison <- HSD.test(model, "Genotype", group=TRUE)
  #print(summary(gl))
    tuk.cld2 <- comparison$groups[,2]
    result_df <- data.frame(
      Genotype = rownames(comparison$groups),
      name = rep(traits[i],4),
      cld = tuk.cld2
    )
  # Store the result data frame in the list
  results_list[[i]] <- result_df
}

#save results for supplmentary table 7 and 8
write.csv(data.table::rbindlist(tukey_list), "Tukey_results_2020_embryo.csv")
write.csv(data.table::rbindlist(anova_list), "ANOVA_results_2020_embryo.csv")


#Formatting data for Visualizations
tukey <- data.table::rbindlist(results_list)
tukey <- tukey[tukey$name %in% c("Total.T", "Total.T3","Total.Carots","Chla"),]
 
#Formatting for plot
#remove Rep, Sample_ID, Description columns
metabolites_df <- metabolites_df[,-c(2,3,5)]
metabolites_df <- metabolites_df %>% pivot_longer(!c(Family, Genotype))
metabolites_df <- metabolites_df[metabolites_df$name %in% c("Total.T", "Total.T3","Total.Carots","Chla"),]
#for annotations get the max observation for that trait
#letters will be place above that location
annotations <- metabolites_df %>%
  group_by(name) %>%
  summarize(value = max(value), .groups = 'drop')

#rename some variables for plotting purposes
annotations <- left_join(tukey, annotations, by = c("name"))
metabolites_df$name <- replace_with_greek(metabolites_df$name)
annotations$name <- replace_with_greek(annotations$name)

#Fix naming for graph
metabolites_df$Tissue <- as.factor(metabolites_df$Family)
metabolites_df$Tissue <- gsub("_.*", "",metabolites_df$Family)
metabolites_df$name <- gsub(".Carots$", " Carotenoids", metabolites_df$name)
metabolites_df$name <- gsub("Chla", "Chlorophyll a", metabolites_df$name)
annotations$name <- gsub(".Carots$", " Carotenoids", annotations$name)
annotations$name <- gsub("Chla", "Chlorophyll a", annotations$name)

#ensure ordering is correct
metabolites_df$Genotype <- factor(metabolites_df$Genotype, level=c('WT', 'por2/por2','por1/+;por2/por2',  'por1/por1;por2/por2'  ))
metabolites_df$name <- factor(metabolites_df$name, levels = c("Total Carotenoids","Total Tocotrienols",  "Total Tocopherols", "Chlorophyll a"))
annotations$name <- factor(annotations$name, levels = c("Total Carotenoids", "Total Tocotrienols", "Total Tocopherols", "Chlorophyll a"))

#plot
ggplot(metabolites_df,aes(x = Genotype, y=value, group=Genotype ,width=.8)) +
  geom_boxplot(aes(fill=Genotype)) + 
  geom_point(aes(colour = Family)) +
  #facet_wrap based on traits
  facet_wrap(~name, scales = "free", ncol = 4,
                strip.position = "top") +
  #add color for the family
    scale_color_manual(values =c("red", "black"))+
   scale_y_continuous(limits = c(0, NA)) +
  guides(color = guide_legend(override.aes = list(size = 7))) +
  #color for plant phenotype
  scale_fill_manual(values =c( "#004D40","#004D40",  "greenyellow","#FFC107"))+
  theme_bw()+
  labs(color = "Family")+
  xlab("")+
  theme(
        legend.text = element_text(size = 10),
          plot.title.position = "plot",
        axis.title=element_text(size=30),
        panel.spacing = unit(4, "lines"),
        strip.text = element_text(size = 20),
               axis.text.x = element_text(size=15,face = "italic",colour = "black",angle = 45,hjust = 1, vjust = 1),
        text = element_text(family = "Helvetica"),
        axis.text.y = element_text(size=15,face="bold",colour = "black",angle = 0))+
  geom_text(data = annotations, aes(label = cld, y = value*1.1), position=position_dodge(width=0.9), color = "black", family= "sans", size = 5) +
  theme(legend.key.size = unit(1, 'cm')) 


ggsave("Figure6a.png", width = 24, height =8, device='png', dpi=700)



```

Figure 6b code chunk:
input: figure6_data.csv
data: 2020  Greenhouse experiment 
Tissue type: 24 DAP endosperm tissue 

```{r figure 6b}
### data from 2022 analysis for 20GH fresh samples
metabolites_df <-  read_xlsx("../data/figure6_data.xlsx", sheet = 2)[,-c(1,5)]
tissues <- c("9.3-41_Embryo","9.3-41_Endosperm","9.3-5_Embryo","9.3-5_Endosperm")
traits <- c("a.T", "d.T", "g.T", "a.T3", "d.T3", "g.T3", "Total.T", "Total.T3", "Total.TT3","Chla", "Total.Carots")
metabolites_df$Genotype <- gsub("-","*",metabolites_df$Genotype)


metabolites_df$Genotype <- gsub("\\+\\*\\*\\*", "por1/+;por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\+\\*", "por1/por1;por2/+", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\*\\*", "por1/por1;por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\+\\+\\*\\*", "por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\+\\+", "por1/por1", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\+\\+\\+\\+", "WT",metabolites_df$Genotype)

results_list <- list()
tukey_list <- list()
anova_list <- list()

metabolites_df <- metabolites_df[metabolites_df$Tissue %in% c("9.3-41_Endosperm","9.3-5_Endosperm"),]

colnames(metabolites_df)[1] <- "Family"

for ( i in 1: length(traits)){
  #get trait (i.e. tocochromonal) and tissue type
  x <-  unlist(as.vector( metabolites_df[,traits[i]]))
  df <- data.frame("TT" = x, "Genotype" = metabolites_df$Genotype, "Family" = as.factor(metabolites_df$Family), rep = as.factor(metabolites_df$Rep))

  df$Genotype <- as.factor(df$Genotype)
  print(traits[i])
  if (sum(df$TT) == 0){
    next
  }

  #print(leveneTest(TT~ Genotype,df))

  # Identify outliers
  model <- lm(TT~ Family*Genotype,df)
  
  options(contrasts = c("contr.sum", "contr.poly"))
  #aov = type 
  outliers <- outlierTest(model, cutoff=0.01, order=TRUE, label = rownames(df))
  #only Outlier is chlorophyll a
  if (outliers$signif){
    
    clean_df <- df[!rownames(df) %in% names(outliers$bonf.p < 0.01), ]
    #statistical tests, remove famiily term to test differences
    model <- lm(TT~ Genotype,df)
    x <- Anova(model, data = df, type = "III")
    
  
    x$trait <- rep(traits[i],3)
    x$comparisons <- row.names(x)

    anova_list[[i]] <- x
   
    comparison <- HSD.test(model, "Genotype", group=F, unbalanced = T)
    tukey_df <- comparison$comparison
    tukey_df$trait <- rep(traits[i],6)
    tukey_df$comparison <- row.names(tukey_df)
    tukey_list[[i]] <- tukey_df
    comparison <- HSD.test(model, "Genotype", group=TRUE, unbalanced = T)
    tuk.cld2 <- comparison$groups[,2]
    result_df <- data.frame(
      Genotype = rownames(comparison$groups),
      name = rep(traits[i],4),
      cld = tuk.cld2
    )
    # Store the result data frame in the list
    results_list[[i]] <- result_df
    next
  }

    x <- Anova(model, data = df, type = "III")

  
    x$trait <- rep(traits[i],5)
    x$comparisons <- row.names(x)

    anova_list[[i]] <- x
   
    comparison <- HSD.test(model, "Genotype", group=F)
    tukey_df <- comparison$comparison
    tukey_df$trait <- rep(traits[i],6)
    tukey_df$comparison <- row.names(tukey_df)
    tukey_list[[i]] <- tukey_df
  #perform Tukey HSD and get letters for plotting
  comparison <- HSD.test(model, "Genotype", group=TRUE)
  #print(summary(gl))
    tuk.cld2 <- comparison$groups[,2]
    result_df <- data.frame(
      Genotype = rownames(comparison$groups),
      name = rep(traits[i],4),
      cld = tuk.cld2
    )
  # Store the result data frame in the list
  results_list[[i]] <- result_df
}

write.csv(data.table::rbindlist(tukey_list), "Tukey_results_2020_endo.csv")
write.csv(data.table::rbindlist(anova_list), "ANOVA_results_2020_endo.csv")



tukey <- data.table::rbindlist(results_list)
tukey <- tukey[tukey$name %in% c("Total.T", "Total.T3","Total.Carots","Chla"),]
 
#Formatting for plot
#remove Rep, Sample_ID, Description columns
metabolites_df <- metabolites_df[,-c(2,3,5)]
metabolites_df <- metabolites_df %>% pivot_longer(!c(Family, Genotype))
metabolites_df <- metabolites_df[metabolites_df$name %in% c("Total.T", "Total.T3","Total.Carots","Chla"),]




#for annotations get the max observation for that trait
#letters will be place above that location
annotations <- metabolites_df %>%
  group_by(name) %>%
  summarize(value = max(value), .groups = 'drop')

#rename some variables for plotting purposes
annotations <- left_join(tukey, annotations, by = c("name"))
metabolites_df$name <- replace_with_greek(metabolites_df$name)
annotations$name <- replace_with_greek(annotations$name)



#Fix naming for graph
metabolites_df$Tissue <- as.factor(metabolites_df$Family)
metabolites_df$Tissue <- gsub("_.*", "",metabolites_df$Family)
metabolites_df$name <- gsub(".Carots$", " Carotenoids", metabolites_df$name)
metabolites_df$name <- gsub("Chla", "Chlorophyll a", metabolites_df$name)
annotations$name <- gsub(".Carots$", " Carotenoids", annotations$name)
annotations$name <- gsub("Chla", "Chlorophyll a", annotations$name)

#ensure ordering is correct
metabolites_df$Genotype <- factor(metabolites_df$Genotype, level=c('WT', 'por2/por2','por1/+;por2/por2',  'por1/por1;por2/por2'  ))
metabolites_df$name <- factor(metabolites_df$name, levels = c("Total Carotenoids","Total Tocotrienols",  "Total Tocopherols", "Chlorophyll a"))
annotations$name <- factor(annotations$name, levels = c("Total Carotenoids", "Total Tocotrienols", "Total Tocopherols", "Chlorophyll a"))
#remove outliers
metabolites_df[metabolites_df$Family == "9.3-41_Endosperm" & metabolites_df$Genotype == "por1/+;por2/por2" & metabolites_df$name == "Chlorophyll a", ]$value <- NA

ggplot(metabolites_df,aes(x = Genotype, y=value ,width=.8)) +
  geom_boxplot(aes(fill=Genotype), show.legend =F) + 
  geom_point(aes(colour = Tissue)) +
    geom_text(data= annotations, aes(label = cld, y = value*1.1), position=position_dodge(width=0.9), color = "black", family= "sans", size = 5) +
  facet_wrap(vars(name), scales = "free", ncol = 4) +

    scale_color_manual(values =c("red", "black")) +
   scale_y_continuous(limits = c(0, NA)) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  scale_fill_manual(values =c( "#004D40","#004D40",  "greenyellow","#FFC107")) +
  theme_bw() +
  labs(color = "Family") +
  xlab("") +
  theme(
        legend.text = element_text(size = 10),
          plot.title.position = "plot",
        axis.title=element_text(size=30),
        panel.spacing = unit(4, "lines"),
        strip.text = element_text(size = 20),
               axis.text.x = element_text(size=20,face = "italic",colour = "black",angle = 45,hjust = 1, vjust = 1),
        axis.text.y = element_text(size=15,face="bold",colour = "black",angle = 0)) +

  theme(legend.key.size = unit(4, 'cm')) 





ggsave("Figure6b.png", width = 24, height =8, device='png', dpi=700)

```

```{r percent increases for embryo tissue}
#calculates percentages for paper
calculate_percent_increase <- function(original_value, new_value) {
  # Calculate the difference
  difference <- new_value - original_value
  
  # Calculate percent increase
  percent_increase <- (difference / original_value) * 100
  
  # Return the percent increase
  return(mean(percent_increase))
}
metabolites_df <- metabolites_df %>% filter(name %in% c("Total Carotenoids", "Total Tocopherols", "Total Tocotrienols", "Chlorophyll a"))
x <- metabolites_df %>% group_by(Genotype,Family, name) %>% dplyr::summarise(mean_values = mean(value))

WT <- x %>% group_by(name,Family) %>% dplyr::mutate(percent = calculate_percent_increase(mean_values[Genotype == "WT"], mean_values[Genotype == "por1/por1;por2/por2"]))

por2 <- x %>% group_by(name,Family) %>% dplyr::mutate(percent = calculate_percent_increase(mean_values[Genotype == "WT"], mean_values[Genotype == "por2/por2"]))

por1 <- x %>% group_by(name,Family) %>% dplyr::mutate(percent = calculate_percent_increase(mean_values[Genotype == "WT"], mean_values[Genotype == "por1/+;por2/por2"]))

por2_compare <- x %>% group_by(name,Family) %>% dplyr::mutate(percent = calculate_percent_increase(mean_values[Genotype == "por2/por2"], mean_values[Genotype == "por1/por1;por2/por2"]))

por1_compare <- x %>% group_by(name,Family) %>% dplyr::mutate(percent = calculate_percent_increase(mean_values[Genotype == "por1/+;por2/por2"], mean_values[Genotype == "por1/por1;por2/por2"]))


x$mean_values[x$Genotype == "WT"] - x$mean_values[x$Genotype == "por1/por1;por2/por2"]

```

Supplemental Figures.

```{r supplemental}
###
metabolites_df <- read_xlsx("../data/figure6_data.xlsx", sheet = 2)[,-c(1,5)]
tissues <- c("9.3-41_Embryo","9.3-41_Endosperm","9.3-5_Embryo","9.3-5_Endosperm")
traits <- c("a.T", "d.T", "g.T", "a.T3", "d.T3", "g.T3", "Total.T", "Total.T3", "Total.TT3","Chla", "Total.Carots")
metabolites_df$Genotype <- gsub("-","*",metabolites_df$Genotype)

#format names for figures
metabolites_df$Genotype <- gsub("\\+\\*\\*\\*", "por1/+;por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\+\\*", "por1/por1;por2/+", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\*\\*", "por1/por1;por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\+\\+\\*\\*", "por2/por2", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\*\\*\\+\\+", "por1/por1", metabolites_df$Genotype)
metabolites_df$Genotype <- gsub("\\+\\+\\+\\+", "WT",metabolites_df$Genotype)

results_list <- list()
#get Embryo tissue
metabolites_df <- metabolites_df[metabolites_df$Tissue %in% c("9.3-41_Embryo","9.3-5_Embryo"),]
colnames(metabolites_df)[1] <- "Family"
for ( i in 1: length(traits)){
  #get trait (i.e. tocochromonal) and tissue type
  x <-  unlist(as.vector( metabolites_df[,traits[i]]))
  
  df <- data.frame("TT" = x, "Genotype" = metabolites_df$Genotype, "Family" = as.factor(metabolites_df$Family), rep = as.factor(metabolites_df$Rep))
  df$Genotype <- as.factor(df$Genotype)
  print(df$Genotype)
  print(traits[i])

  #print(leveneTest(TT~ Genotype,df))

  # Identify outliers
  model <- lm(TT~ Family*Genotype,df)
  outliers <- outlierTest(model, cutoff=0.05, order=TRUE, label = rownames(df))
  #remove outlies
  if (outliers$signif) {
      print("please")
    clean_df <- df[!rownames(df) %in% names(outliers$bonf.p < 0.01), ]
    model <- lm(TT~ Genotype, clean_df)
    x <- aov(TT~ Genotype, clean_df)
    comparison <- HSD.test(model, "Genotype", group=TRUE)
  #print(summary(gl))
    tuk.cld2 <- comparison$groups[,2]
    result_df <- data.frame(
      Genotype = rownames(comparison$groups),
      name = rep(traits[i],4),
      cld = tuk.cld2
    )
    # Store the result data frame in the list
    removed_results_list[[i]] <- result_df
    next
  }

 
  #perform Tukey HSD and get letters for plotting
  comparison <- HSD.test(model, "Genotype", group=TRUE)
  #print(summary(gl))
    tuk.cld2 <- comparison$groups[,2]
    result_df <- data.frame(
      Genotype = rownames(comparison$groups),
      name = rep(traits[i],4),
      cld = tuk.cld2
    )
  # Store the result data frame in the list
  results_list[[i]] <- result_df
}


tukey <- data.table::rbindlist(results_list)
tukey <- tukey[!(tukey$name %in% c("Total.TT3","Total.Carots","Chla")),]
tukey$name <- replace_with_greek(tukey$name)
#Formatting for plot
#remove Rep, Sample_ID, Description columns
metabolites_df <- metabolites_df[,-c(2,3,5)]
metabolites_df <- metabolites_df %>% pivot_longer(!c(Family, Genotype))
metabolites_df <- metabolites_df[!(metabolites_df$name %in% c("Total.TT3","Total.Carots","Chla")),]
metabolites_df$name <- replace_with_greek(metabolites_df$name)

#for annotations get the max observation for that trait
#letters will be place above that location
annotations <- metabolites_df %>%
  group_by(name) %>%
  summarize(value = max(value), .groups = 'drop')

#rename some variables for plotting purposes
annotations <- left_join(tukey, annotations, by = c("name"))


metabolites_df$Tissue <- as.factor(metabolites_df$Family)
metabolites_df$Tissue <- gsub("_.*", "",metabolites_df$Family)
metabolites_df$name <- gsub(".Carots$", " Carotenoids", metabolites_df$name)

annotations$name <- gsub(".Carots$", " Carotenoids", annotations$name)

metabolites_df$Genotype <- factor(metabolites_df$Genotype, level=c('WT', 'por2/por2','por1/+;por2/por2',  'por1/por1;por2/por2'  ))


metabolites_df$name <- factor(metabolites_df$name, levels = c( "α-Tocotrienol" ,"δ-Tocotrienol","γ-Tocotrienol", "Total Tocotrienols", "α-Tocopherol" , "δ-Tocopherol" ,"γ-Tocopherol",      "Total Tocopherols"))
annotations$name <- factor(annotations$name, levels = c( "α-Tocotrienol" ,"δ-Tocotrienol","γ-Tocotrienol", "Total Tocotrienols", "α-Tocopherol" , "δ-Tocopherol" ,"γ-Tocopherol",      "Total Tocopherols"))

#plot
ggplot(metabolites_df,aes(x = Genotype, y=value, group=Genotype ,width=.8)) +
  geom_boxplot(aes(fill=Genotype), show.legend = F) + 
  geom_point(aes(colour = Family), show.legend = F) +
  #facet_wrap based on traits
  facet_wrap(~name, scales = "free_y", ncol = 4,
                strip.position = "top") +
  #add color for the family
    scale_color_manual(values =c("red", "black"))+
   scale_y_continuous(limits = c(0, NA)) +
  guides(color = guide_legend(override.aes = list(size = 7))) +
  #color for plant phenotype
  scale_fill_manual(values =c( "#004D40","#004D40",  "greenyellow","#FFC107"))+
  theme_bw()+
  labs(color = "Family")+
  xlab("")+
  theme(
        legend.text = element_text(size = 10),
          plot.title.position = "plot",
        axis.title=element_text(size=30),
        panel.spacing = unit(4, "lines"),
        strip.text = element_text(size = 20),
               axis.text.x = element_text(size=15,face = "italic",colour = "black",angle = 45,hjust = 1, vjust = 1),
        text = element_text(family = "Helvetica"),
        axis.text.y = element_text(size=15,face="bold",colour = "black",angle = 0))+
  geom_text(data = annotations, aes(label = cld, y = value*1.1), position=position_dodge(width=0.9), color = "black", family= "sans", size = 5) +
  theme(legend.key.size = unit(8, 'cm')) 


ggsave("Figure S18.png", width = 24, height =12, device='png', dpi=700)



```
